Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-04-10 paper.Rmd
paper edit

2.  access to teaching materials for skills that are in high demand and aligned with employers\' needs.

@@

The set of developed tutorials consists of the following tutorials:

@@

The tutorials are publicly hosted on GitHub (<https://github.com/ABMArchaeologists/ABMA_tutorials/>). Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced ([https://ABMArchaeologists.github.io/ABMA_Website](https://ABMArchaeologists.github.io/ABMA_Website/#/){.uri}). On this website, the tutorials can be followed without the need to download any software.

>>>>

2.  access to teaching materials for skills that are in high demand and aligned with employers' needs.

@@

The final tutorals are available for download at <https://github.com/ABMArchaeologists/ABMA_tutorials> and are citeable [@rocks-macqueen2024]. The set of developed tutorials consists of the following tutorials:

@@

The tutorials are publicly hosted on GitHub (<https://github.com/ABMArchaeologists/ABMA_tutorials/>) and are citeable [@jutte2024]. Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced ([https://ABMArchaeologists.github.io/ABMA_Website](https://ABMArchaeologists.github.io/ABMA_Website/#/){.uri}). On this website, the tutorials can be followed without the need to download any software.

### 2024-04-10 paper.tex
paper edit

\title{Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists}
\author{true \and true \and true \and true \and true \and true \and true \and true \and true}
\date{April 03, 2024}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  increased quality of education and training in the areas of ABM that are free and open;
\item
  access to teaching materials for skills that are in high demand and aligned with employers\textquotesingle{} needs.
\end{enumerate}

@@

The set of developed tutorials consists of the following tutorials:

@@

The tutorials are publicly hosted on GitHub (\url{https://github.com/ABMArchaeologists/ABMA_tutorials/}). Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced (\href{https://ABMArchaeologists.github.io/ABMA_Website/\#/}{https://ABMArchaeologists.github.io/ABMA\_Website}). On this website, the tutorials can be followed without the need to download any software.

@@

@@

>>>>

\title{Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists}
\author{true \and true \and true \and true \and true \and true \and true \and true \and true}
\date{April 10, 2024}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  increased quality of education and training in the areas of ABM that are free and open;
\item
  access to teaching materials for skills that are in high demand and aligned with employers' needs.
\end{enumerate}

@@

The final tutorals are available for download at \url{https://github.com/ABMArchaeologists/ABMA_tutorials} and are citeable (Rocks-Macqueen et al. 2024). The set of developed tutorials consists of the following tutorials:

@@

The tutorials are publicly hosted on GitHub (\url{https://github.com/ABMArchaeologists/ABMA_tutorials/}) and are citeable (Jutte et al. 2024). Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced (\href{https://ABMArchaeologists.github.io/ABMA_Website/\#/}{https://ABMArchaeologists.github.io/ABMA\_Website}). On this website, the tutorials can be followed without the need to download any software.

@@

\leavevmode\vadjust pre{\hypertarget{ref-jutte2024}{}}%
Jutte, A, Aalpoel, R, Baan, E, Regts, S, Lucas, S, Mulder, J, Sijbrant, A, Visser, RM, Rocks-Macqueen, D, Knaap, L van der, Romanowska, I, Brughmans, T, Lambers, K and Aitchison, K. 2024. \emph{Agent based modelling for archaeologists: Website source}. Zenodo. DOI: https://doi.org/\href{https://doi.org/10.5281/zenodo.10931759}{10.5281/zenodo.10931759}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-rocks-macqueen2024}{}}%
Rocks-Macqueen, D, Knaap, L van der, Romanowska, I, Jutte, A, Visser, RM, Brughmans, T, Lambers, K and Aitchison, K. 2024. \emph{Agent based modelling for archaeologists: tutorials}. Zenodo. DOI: https://doi.org/\href{https://doi.org/10.5281/zenodo.10931587}{10.5281/zenodo.10931587}.
